\modLP{Identification of} Biological Regulatory Networks from Process Hitting models

### 2014-10-30 parts-tr2global.tex
section 4.1
fix Def 11

For the inference of the interaction graph and Thomas parameters from a PH model, the following
sections assume that \emph{all the cooperative sorts are deterministic}.
\todo{add more explanation depending on the text of the next sections}

@@

\modLP{%
If the cooperative sorts are all deterministic (\pref{def:deterministic-sort}),
it is sufficient to specify the configuration $\sigma$ of a group $g$ of regulators of a sort $a$
to obtain the configuration of all the sorts hitting $a$ directly.
Indeed, because of the absence of cycles between cooperative sorts
(\pref{pro:wf-ph}), one can recursively
evaluate the focal process of each cooperative sort that hit $a$ with respect to
the configuration $\sigma$ of the regulators $g$.
Such an extended configuration is denoted by $\ctx_a^g(\sigma)$, formalized in
\pref{def:ctx-sigma}
\begin{definition}[Configuration extension $\ctx_a^g(\sigma)$]
\label{def:ctx-sigma}
Given $a\in\PHs$, a group $g\in X(a)$ and a configuration 
$\sigma\in L(g)$, $\ctx_a^g(\sigma)$ is the configuration $\sigma$ with the corresponding
processes of the cooperative sorts in $\PHdirectpredec{a}$:
\begin{align}
\ctx_a^g(\sigma) & \DEF \sigma \uplus \state{\upsilon(\sigma) \mid\upsilon \in\PHdirectpredec{a} \cap \CSorts} 
\label{eq:ctx-sigma}
\\
\upsilon(\sigma') & \DEF
\begin{cases}
\focals(\upsilon,L_\upsilon,\sigma') & \text{if
$\PHdirectpredec{\upsilon}\subseteq\f{dom}(\sigma')$}
\\
\upsilon(\sigma' \uplus \state{\upsilon'(\sigma') \mid 
  \upsilon'\in\PHdirectpredec{\upsilon} \cap \CSorts })
  & \text{otherwise.}
\end{cases}
\label{eq:cooperative-eval}
\end{align}
\end{definition}
}

>>>>

For the inference of the interaction graph and Thomas parameters from a PH model, the following
sections assume that \emph{all the cooperative sorts are deterministic}.

@@

\modLP{%
If the cooperative sorts are all deterministic (\pref{def:deterministic-sort}),
it is sufficient to specify the configuration $\sigma$ of a group $g$ of regulators of a sort $a$
to obtain the configuration of all the sorts hitting $a$ directly.
Indeed, because of the absence of cycles between cooperative sorts
(\pref{pro:wf-ph}), one can recursively
evaluate the focal process of each cooperative sort that hit $a$ with respect to
the configuration $\sigma$ of the regulators $g$.
Such an extended configuration is denoted by $\ctx_a^g(\sigma)$, formalized in
\pref{def:ctx-sigma}
\begin{definition}[Configuration extension $\ctx_a^g(\sigma)$]
\label{def:ctx-sigma}
Given $a\in\PHs$, a sub-set of regulators $g\subset \PHpredecgene{a}$ and a configuration 
$\sigma\in L(g)$, $\ctx_a^g(\sigma)$ is the configuration $\sigma$ with the corresponding
processes of the cooperative sorts in $\PHdirectpredec{a}$:
\begin{align}
\ctx_a^g(\sigma) & \DEF \sigma \uplus \state{\upsilon(\sigma) \mid\upsilon \in\PHdirectpredec{a} \cap \CSorts} 
\label{eq:ctx-sigma}
\\
\upsilon(\sigma') & \DEF
\begin{cases}
\focals(\upsilon,L_\upsilon,\sigma') & \text{if
$\PHdirectpredec{\upsilon}\subseteq\f{dom}(\sigma')$}
\\
\upsilon(\sigma' \uplus \state{\upsilon'(\sigma') \mid 
  \upsilon'\in\PHdirectpredec{\upsilon} \cap \CSorts })
  & \text{otherwise,}
\end{cases}
\label{eq:cooperative-eval}
\end{align}
where $\f{dom}(\sigma')$ is the set of sorts defined in $\sigma'$.
\end{definition}
}

\begin{example}
\todo{}
\end{example}
